Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-03-14 documents/ms.tex
cleaning up figure directory and getting ready to submit

\item{We assign a quality metric $Q_i$ to each of these candidate
periods, as follows.  First, we model the ACF as a function of lag
time $t$ as a damped oscillator with fixed period $T_i$:
\begin{equation}
y = A e^{-t/\tau} \cos{\frac{2\pi t}{T_i} },
\end{equation}
and find the best-fitting parameters $A_i$ and $\tau_i$ by a non-linear
least squares minimization procedure--though enforcing a maximum
value of $\tau = 20 * P_i/T_i$ to avoid unreasonably
large solutions of $\tau.  We then define the
following heuristic quality metric:
\begin{equation}
\label{eq:quality}
Q_i = \left(\frac{\tau_i}{T_i}\right) \left(\frac{N_i h_i}{R_i}\right),
\end{equation}
where $h_i$ is the height of the ACF peak at $T_i$,
$N_i$ is the length of the lag vector in the ACF (directly proportional
to the maximum allowed period $P_i$),
and $R_i$ is the sum of squared residuals between the
damped oscillator model and the actual ACF data.  The idea behind this
quality metric is to give a candidate period a higher score if

>>>>

\item{We assign a quality metric $Q_i$ to each of these candidate
periods, as follows.  First, we model the ACF as a function of lag
time $t$ as a damped oscillator with fixed period $T_i$:
\begin{equation}
y = A e^{-t/\tau} \cos{\frac{2\pi t}{T_i} },
\end{equation}
and find the best-fitting parameters $A_i$ and $\tau_i$ by a non-linear
least squares minimization procedure--though enforcing a maximum
value of $\tau = 20 * P_i/T_i$ to avoid unreasonably
large solutions of $\tau$.
We then define the following heuristic quality metric:
\begin{equation}
\label{eq:quality}
Q_i = \left(\frac{\tau_i}{T_i}\right) \left(\frac{N_i h_i}{R_i}\right),
\end{equation}
where $h_i$ is the height of the ACF peak at $T_i$,
$N_i$ is the length of the lag vector in the ACF (directly proportional
to the maximum allowed period $P_i$),
and $R_i$ is the sum of squared residuals between the
damped oscillator model and the actual ACF data.  The idea behind this
quality metric is to give a candidate period a higher score if
